Prediction of 2024 US election ...

### 2024-11-03 paper/paper.qmd
fixed graph axis labels

graph_data %>% filter(!is.na(pollscore) & !is.na(sample_size)) %>% 
  ggplot(aes(x = pollscore, y = sample_size)) +
  geom_point(alpha = 0.33) + geom_smooth(method = "lm", se = FALSE, color = light_red)

>>>>

graph_data %>% filter(!is.na(pollscore) & !is.na(sample_size)) %>% 
  ggplot(aes(x = pollscore, y = sample_size)) +
  geom_point(alpha = 0.33) + geom_smooth(method = "lm", se = FALSE, color = light_red) +
  labs(x = "Poll Score", y = "Poll Sample Size")
